---
title: "Re-working a Graph: Employed and Happy"
output: html_notebook
---

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
```


Import the dataset
```{r}
employed_and_happy <- read_csv("employed_and_happy.csv")
employed_and_happy
```

# How can we graph the data?
```{r echo=TRUE}
ggplot(employed_and_happy) +
  geom_bar(aes(x = `Aspects of Job`, y = `Percent Satisfied`, fill = `Field of Study`), stat = "identity", position = "dodge") + 
  coord_flip() +
  guides(fill = guide_legend(reverse = TRUE))
```


```{r echo=TRUE}
ggplot(employed_and_happy) +
  geom_bar(aes(x = `Aspects of Job`, y = `Percent Satisfied`, fill = `Field of Study`), stat = "identity", position = "dodge") + 
  coord_flip() +
  guides(fill = guide_legend(reverse = TRUE)) +
  scale_fill_manual(values = c("red", "grey10", "grey30", "grey50", "grey70", "red"))
```

# Manually reorder the "Field of Study"

```{r echo=TRUE}
employed_and_happy_b <- employed_and_happy %>% mutate(Degree = factor(`Field of Study`, levels = c("Business", "Education", "Engineering", "Health or Medical Sciences", "Humanities", "Arts")))

employed_and_happy_b
```

```{r echo=TRUE}
ggplot(employed_and_happy_b) +
  geom_bar(aes(x = `Aspects of Job`, y = `Percent Satisfied`, fill = `Degree`), stat = "identity", position = "dodge") + 
  coord_flip() +
  guides(fill = guide_legend(reverse = TRUE)) +
  scale_fill_manual(values = c("grey30", "grey40", "grey50", "grey60", "#a1d99b", "#31a354")) +
  theme(legend.position = "bottom")
```


# Very close to what I want; however, I want to sort the data by highest value in Humanities 

```{r echo=TRUE}
employed_and_happy_c <- employed_and_happy_b %>% mutate(Aspects = factor(`Aspects of Job`, levels = c("Opportunities for Advancement", "Salary", "Benefits", "Job Security", "Job Location")))
employed_and_happy_c

ggplot(employed_and_happy_c) +
  geom_bar(aes(x = `Aspects`, y = `Percent Satisfied`, fill = `Degree`), stat = "identity", position = "dodge") + 
  coord_flip() +
  guides(fill = guide_legend(reverse = TRUE)) +
  scale_fill_manual(values = c("grey40", "grey50", "grey60", "grey70", "#a1d99b", "#31a354")) +
  theme(legend.position = "bottom", legend.title = element_blank())
```

# Finally, I'm going to change the theme to remove the grey background

```{r echo=TRUE}
ggplot(employed_and_happy_c) +
  geom_bar(aes(x = `Aspects`, y = `Percent Satisfied`, fill = `Degree`), stat = "identity", position = "dodge") + 
  scale_y_continuous(limits = c(0,100)) +
  coord_flip() +
  guides(fill = guide_legend(reverse = TRUE)) +
  scale_fill_manual(values = c("grey40", "grey50", "grey60", "grey70", "#a1d99b", "#31a354")) +
  theme_bw() +
  theme(legend.position = "bottom", legend.title = element_blank())
```


# I was curious to see what the graphic would look like if Degrees were placed on the y axis

```{r echo=TRUE}
ggplot(employed_and_happy_c) +
  geom_bar(aes(x = `Degree`, y = `Percent Satisfied`, fill = `Aspects`), stat = "identity", position = "dodge") + 
  coord_flip() +
  guides(fill = guide_legend(reverse = TRUE)) +
  theme_bw() + 
  theme(legend.position = "bottom", legend.title = element_blank()) +
  scale_fill_brewer(palette = "Blues") + 
  annotate("rect", xmin = 4.5, xmax = 6.5, ymin = 0, ymax = 100, colour = "red",  fill = "NA", alpha = 0.2)
```

Using the **JavaScript** JS array at [colorbrewer2.org](http://colorbrewer2.org/#type=sequential&scheme=Greens&n=6)


```{r echo=TRUE}
ggplot(employed_and_happy_c) +
  geom_bar(aes(x = `Degree`, y = `Percent Satisfied`, fill = `Aspects`), stat = "identity", position = "dodge") + 
  coord_flip() +
  guides(fill = guide_legend(reverse = TRUE)) +
  theme_bw() + 
  theme(legend.position = "bottom", legend.title = element_blank()) +
  scale_fill_manual(values = c('#edf8e9','#c7e9c0','#a1d99b','#74c476','#31a354','#006d2c')) +
  annotate("rect", xmin = 4.5, xmax = 6.5, ymin = 0, ymax = 100, colour = "red",  fill = "NA", alpha = 0.2)
```

